Fast-Match: Fast and robust feature matching on large images

### 2014-11-09 paper.tex
Added images & fixed sentence
Added support for statement

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
%===========================================================
\begin{document}
%\pagestyle{headings}

% TODO: Insert submission number
\def\ACCV14SubNumber{***}  % Insert your submission number here

%===========================================================
\title{Fast-Match: Fast and robust feature matching on large images}

@@

%===========================================================

@@

Lowe and others have shown that the distance between two SIFT descriptors is much less indicative of a true correspondence than the ratio between the best and second best match \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}. This ratio is more formally defined as follows: If we let $f_q$ be a feature in the \emph{query image} and $f_t, f_b$ be the two nearest neighbours of $f_q$ in the \emph{target image} then the ratio $r$ is defined as follows:
\begin{align*}
    r %\text{r}(f_{q}, (f_t, f_b)) \\
        &= \frac{d(f_{q}, f_{t})}{d(f_{q}, f_{b})}.
\end{align*}
Here $d(f_i,f_j)$ is the distance between the features $f_i$ and $f_j$. For SIFT this is the Euclidean distance. The distance between two feature points is greater when the feature points resemble each other less. For this reason we have higher confidence in a match with a low $r$-value. Using $r$ as a measure of match confidence presumes that we expect each feature in the \emph{target image} to have at most one true correspondence in the \emph{target image}. Intuitively if we try to find a match for a feature $f_i$ in an image that does not have any true correspondences, then we would expect the two closest neighbours to be roughly equally well matched with $f_i$. For this reason we attribute high confidence to matches where the closest neighbour is dramatically closer to $f_i$ than the second closest neighbour and discard the rest.

@@

We compare the algorithm to the standard \emph{Ratio-Match} \cite{lowe2004sift} as well as the newer \emph{Mirror-Match} \cite{arnfred2013mirror}. We exclude the geometric algorithms discussed in related works from comparison because even the fastest cases are two to three magnitudes slower than \emph{Ratio-Match} and as such are too time consuming to use when matching features in large images. Both \emph{Ratio-Match} and \emph{Mirror-Match} however have shown good results in matching applications while both being fast enough to compare on larger images.

>>>>

\begin{document}
% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\title{Fast-Match: Fast and robust feature matching on large images}

@@

@@

Lowe and others have shown that the distance between two SIFT descriptors is much less indicative of a true correspondence than the ratio between the best and second best match \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}. This ratio is more formally defined as follows: If we let $f_q$ be a feature in the \emph{query image} and $f_t, f_b$ be the two nearest neighbours of $f_q$ in the \emph{target image} then the ratio $r$ is defined as follows:
\begin{align*}
    r %\text{r}(f_{q}, (f_t, f_b)) \\
        &= \frac{d(f_{q}, f_{t})}{d(f_{q}, f_{b})}.
\end{align*}
Here $d(f_i,f_j)$ is the distance between the features $f_i$ and $f_j$. For SIFT this is the Euclidean distance. The distance between two feature points is greater when the feature points resemble each other less. For this reason we have higher confidence in a match with a low $r$-value. Using $r$ as a measure of match confidence presumes that we expect each feature in the \emph{target image} to have at most one true correspondence in the \emph{target image}. Intuitively if we try to find a match for a feature $f_i$ in an image that does not have any true correspondences, then we would expect the two closest neighbours to be roughly equally well matched with $f_i$. The effectiveness of \emph{Ratio-Match} over a naïve nearest neighbor match (\cite{lowe2004sift, mikolajczyk2005performance}) supports this notion. For this reason we attribute high confidence to matches where the closest neighbour is dramatically closer to $f_i$ than the second closest neighbour and discard the rest.

@@

We compare the algorithm to the standard \emph{Ratio-Match} \cite{lowe2004sift} as well as the newer \emph{Mirror-Match} \cite{arnfred2013mirror}. We exclude the geometric algorithms discussed in related works from comparison because even the fastest cases are two to three magnitudes slower than \emph{Ratio-Match} and as such are too time consuming to use when matching features in large images.
